\documentclass[9pt]{article}

\usepackage{mathtext}         % если нужны русские буквы в формулах (не обязательно)
\usepackage[T2A]{fontenc}     % внутренняя T2A кодировка TeX
\usepackage[russian]{babel}   % включение переносов
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}
\pagestyle{empty} % нумерация выкл.
\addtolength{\textheight}{1.75in}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{color}
\usepackage{setspace}
\usepackage{multicol}
\setlength{\columnsep}{30pt}
\usepackage{fontawesome}
\setlength\parindent{0em}
\usepackage{xcolor}

\definecolor{gray}{rgb}{0.4,0.4,0.4}
\definecolor{mylinkcolor}{HTML}{2200CC}

\hypersetup{
    colorlinks=true,
    urlcolor=mylinkcolor
}

\begin{document}

\begin{multicols}{2}

\noindent
\vspace{3em}
\noindent

{\huge{\textbf{Liudmila Kornilova}}}

Software Developer

Berlin, Germany

\vspace{1em}

\href{https://github.com/kornilova203}{github.com/kornilova203}

\href{https://t.me/kornilova203}{t.me/kornilova203}

kornilova203@gmail.com

\vspace{5em}

{\textbf{Talks}}
\vspace{0.5em}
\hrule
\vspace{1em}

{\textbf{MongoDB Tools Everywhere}}

\color{gray} MongoDB World 2020 \color{black}

\href{https://www.mongodb.com/presentations/mongodb-tools-everywhere}{mongodb.com/presentations/mongodb-tools-everywhere}

\vspace{0.3em}

Max Marcon, Liudmila Kornilova

\vspace{0.3em}

Presented the latest additions and enhancements to the ecosystem of tools for MongoDB including new Java driver.

\vspace{2em}
{\textbf{Skills}}
\vspace{0.5em}
\hrule
\vspace{1em}

Java, Kotlin, database management tools, memory and performance profiling

\vspace{0.5em}

{\textbf{Also worked with:}} C++, Python, JavaScript, concurrency


\vspace{2em}
{\textbf{Personal Projects}}
\vspace{0.5em}
\hrule
\vspace{1em}

{\textbf{Matlab/Octave support for JetBrains IDEs}}

\href{https://github.com/kornilova203/matlab-IntelliJ-plugin}{github.com/kornilova203/matlab-IntelliJ-plugin}

\vspace{0.3em}

Plugin adds support for Matlab and Octave languages. It provides syntax highlighting, code completion, resolve, refactorings.

\vspace{2em}
{\textbf{Education}}
\vspace{0.5em}
\hrule
\vspace{1em}

{\textbf{ITMO University}} \color{gray} Saint Petersburg, Russia \color{black}

\color{gray} 2014 - 2018 bachelor \color{black}
\vspace{0.3em}

Faculty of Software Engineering and Computer Systems

Bachelor’s thesis: Computer Search of Distributed Algorithms

\href{https://github.com/kornilova203/synthesis-of-local-algorithms}{github.com/kornilova203/synthesis-of-local-algorithms}


\vspace{2em}

{\textbf{Aalto University}} \color{gray} Helsinki, Finland \color{black}

\color{gray} 2017 - 2018 exchange student \color{black}
\vspace{0.3em}

Department of Computer Science


\columnbreak

\vspace{0.5em}

{\textbf{Experience}}

\vspace{0.5em}

\hrule

\vspace{1em}

{\textbf{JetBrains | DataGrip team | Software Developer}}

\color{gray} September 2018 - present | Berlin, Germany \color{black}

\vspace{0.3em}

\href{https://www.jetbrains.com/datagrip/}{DataGrip} - a cross-platform IDE for databases.

\begin{itemize}
\item \href{https://www.jetbrains.com/datagrip/whatsnew/2019-3/#version-2019-3-mongodb-support}{MongoDB integration}. Implemented JDBC driver and supported \href{https://www.jetbrains.com/datagrip/whatsnew/2021-1/#version-2021-1-data-editor}{document data editing}. Re-implemented DML code-generator so now it’s easy to add code generation for any database script language.
\item Collaborated with MongoDB team and created a Java driver that executes MongoDB JavaScript commands. Java \(\leftrightarrow\) JS interop.

\href{https://github.com/mongodb-js/mongosh/tree/main/packages/java-shell}{github.com/mongodb-js/mongosh}
\item \href{https://www.jetbrains.com/datagrip/whatsnew/2019-2/#version-2019-2-full-text-search}{Full-text search} that helps users to find data in database. It generates correct predicates for lots of different data types and uses search indexes.
\item Cassandra, Hive integration: SQL dialects, resolve, introspection.
\item Redesigned \href{https://www.jetbrains.com/datagrip/whatsnew/2021-3/#importexport}{import UI} and implemented an ability to \href{https://www.jetbrains.com/datagrip/whatsnew/2022-1/#importexport}{copy multiple tables at the same time}.
\item Lot's of table data editor and performance improvements.
\item Interns mentorship. One of my intern's projects was \href{https://www.jetbrains.com/datagrip/whatsnew/2020-3/#version-2020-3-sql-for-mongodb}{SQL for MongoDB}.
\end{itemize}

\vspace{1em}

{\textbf{Google Summer of Code | Scala Native}}

\color{gray} May - August 2018 | Remote \color{black}

\href{https://github.com/scala-native/scala-native-bindgen}{github.com/scala-native/scala-native-bindgen}

\vspace{0.3em}

Implemented Scala Native Bindings Generator.
Bindgen parses C header file and generates Scala class that allows to call native libs from Scala Native code.

\vspace{1.5em}

{\textbf{Eniram | Software Developer}}

\color{gray} March - May 2018 | Helsinki, Finland \color{black}

\vspace{0.3em}

Developed internal-use software that gives access to data collected from cargo ships and calculates various aggregates.

\vspace{1.5em}

{\textbf{JetBrains | Intern}}

\color{gray} June - August 2017 | Saint Petersburg, Russia \color{black}

\href{https://github.com/kornilova203/FlameViewer}{github.com/kornilova203/FlameViewer}

\vspace{0.3em}

Implemented instrumentation Java profiler and a tool that visualized data collected by profilers.

\begin{itemize}
\item Profiler uses ASM library for Java bytecode manipulation.
\item Protobuf is used for data serialization and client-server communi- cation.
\item Web application visualized data on canvas, it is faster that divs or svg graphics.
\end{itemize}





\end{multicols}

\end{document}             % End of document.
